Constructing the transition graphs of interacting hysterons

### 2022-06-09 Paper_draft.tex
Added reasoning for l=3 graphs from l=2 & generalization

\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{.png}
%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
%    \label{fig:linear_coupling}
%\end{figure}\\
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}
%\bibliography{apssamp}% Produces the bibliography via BibTeX.

>>>>

Thus far, we have only considered avalanches of length $l=2$. We now describe how we construct graphs that have avalanches of length $l=3$ based on the graphs that have only $l=2$.\\
Suppose that we have a graph containing only $l=2$ avalanches. Similarly to how we can find $l=2$ avalanches for a base graph by evaluating combinations of incoming and outgoing transitions from the state $S^{(1)}$, we can construct possible $l=3$ avalanches by finding all combinations of $l=2$ avalanches and outgoing $l=1$ transitions for the given graph. From the possible $l=3$ avalanches, we can again construct a list of candidate graphs.\\
We now ask which $l=2$ graphs should be used as our new 'base' for the $l=3$ graphs. It is insufficient to use only the $l=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
We observe that, when extending a $l=2$ avalanche to a $l=3$ avalanche, most of the conditions required for the $l=2$ avalanche are still included in the conditions for the $l=3$ avalanche (see SI). The only exception is the final set of relaxation inequalities that describes the stability of the state $S^{(2)}$, which is stable for the $l=2$ transition but unstable for the $l=3$ transition. As a result, we can predict that for a $l=2$ graph of which any of the first $l-1$ relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\
We can thus distinguish three groups of $l=2$ graphs, as indicated in Fig. \ref{fig:N2l2}. The first group of graphs is realizable, and can therefore also be used as a base to construct $l=3$ graphs. For the second group, the graphs themselves are not realizable, but derived $l=3$ graphs may be realizable. For the third group, neither the $l=2$ graphs themselves nor any derived graphs containing longer avalanches are realizable. To construct all possible $l=3$ graphs, we only need to use graphs from the first two groups.\\
We now generalize our method. To find all graphs with avalanches of length $l$, we construct the graphs for $l-1$, and divide the graphs into the three groups as described. We then construct all possible $l=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups. We can thus iterate over $l$ to find all possible graphs. Our algorithm terminates when none of the graphs belonging to the first and second groups have any possible avalanches of length $l$.

\section{Application to specific models}
We now illustrate how the base graph method is applied to the specific model where the coupling between hysterons is linear. Linear coupling entails that the switching fields $U_i^{+, -}(S)$ depend on the state $S$ as:
\begin{equation}
    U_i^{+, -}(S) = u_i^{+, -} -\sum_{i \neq j}c_{ij}s_j
\end{equation}
Depending on the system, the allowed coupling coefficients $c_{ij}$ may be restricted. We consider two instances of the linear model for $N=3$. First, we look at the case where only one of the coupling coefficients $c_{ij}$ is unequal to zero. Second, we look at a model for hysterons in series, where the coupling is $c_{ij}  = c_j$ with all $c_j < 0$.\\
\subsection{Linear coupling}
%\begin{figure}[!ht]
%    \centering
%    \includegraphics[width=0.5\textwidth]{.png}
%    \caption{Overview of possible scrambling and avalanches in the linear model for a single nonzero $c_ij$.}
%    \label{fig:linear_coupling}
%\end{figure}\\
\subsection{Hysterons in series}
\section{Discussion}
\section{Outlook}
%\bibliography{apssamp}% Produces the bibliography via BibTeX.
